Molecular Gas Dynamics of the strongly-lensed wet-merger RXS J1131$-$1231 at $z$=0.654

### 2016-08-10 WRITEUP/ms.tex
detected CO should be ~30 instead of 70

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------
\section{Introduction}
Studies of galaxy evolution have been focusing on the interplay between
\SF and active galactic nucleus (AGN) activity across cosmic epochs.
It is not well-understood when and how stellar populations of present-day galaxies were assembled,
but it is clear that both the co-moving \SF rate and black hole accretion rate densities
increased substantially since $z$\,$>\,3$ and reached their climax at $z$\ssim$2$, followed by
a rapid decline toward $z$\ssim$0$ \citep[\eg][]{Hopkins06a, Madau14a}.
% Studying the cold gas at the redshift range 0.2 $<$\,$z$\,$<$\,1 of paramount importance to ravel the cause for this decline.
A leading explanation for this decline is related to the evolution of molecular gas content and
\SF efficiency \citep[]{Erb06a, CW13, Walter14a},
but confirmation from direct molecular gas measurements at intermediate redshift
$(0.2\,<\,z\,<\,1)$ is still limited both in number and in the variety of galaxy populations probed ---
only unresolved CO observations have been carried out for $\sim$$70$ ULIRGs up to date \citep{Combes11a, Combes13a}.

>>>>

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------
\section{Introduction}
Studies of galaxy evolution have been focusing on the interplay between
\SF and active galactic nucleus (AGN) activity across cosmic epochs.
It is not well-understood when and how stellar populations of present-day galaxies were assembled,
but it is clear that both the co-moving \SF rate and black hole accretion rate densities
increased substantially since $z$\,$>\,3$ and reached their climax at $z$\ssim$2$, followed by
a rapid decline toward $z$\ssim$0$ \citep[\eg][]{Hopkins06a, Madau14a}.
% Studying the cold gas at the redshift range 0.2 $<$\,$z$\,$<$\,1 of paramount importance to ravel the cause for this decline.
A leading explanation for this decline is related to the evolution of molecular gas content and
\SF efficiency \citep[]{Erb06a, CW13, Walter14a},
but confirmation from direct molecular gas measurements at intermediate redshift
$(0.2\,<\,z\,<\,1)$ is still limited both in number and in the variety of galaxy populations probed ---
only unresolved CO observations have been carried out for $\sim$$30$ ULIRGs up to date \citep{Combes11a, Combes13a}. %18+15
